Seasonality in governing dynamics at submesoscales

### 2016-06-10 writeup/rocha_etal.tex
Adds small technical detail

To better understand the projection of these flows onto different horizontal
scales, we calculate wavenumber spectra of kinetic energy and sea-surface height
(SSH) variance.  Before calculating the spectra, time-mean and spatial linear
trends were removed, and the ensuing fields were multiplied by a Hanning spectral ``window''.
We discuss only spectra for the 1/48$^\circ$, which simply extends the 1/24$^\circ$
towards smaller scales (supplemental material).

>>>>

To better understand the projection of these flows onto different horizontal
scales, we calculate wavenumber spectra of kinetic energy and sea-surface height
(SSH) variance.  Before calculating the spectra, time-mean and spatial linear
trends were removed, and the ensuing fields were multiplied by a two-dimensional Hanning spectral ``window''.
The two-dimensional spectra were averaged azimuthly \citep[e.g., ][]{rocha_etal2016} .We discuss only spectra for the 1/48$^\circ$, which simply extends the 1/24$^\circ$
towards smaller scales (supplemental material).
